Lasso_RCI_Response

### 2024-04-29 Lasso_RCI_Response.Rmd
Fixed exclusion.

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
  ))
Mothership_lasso_1 <- na.omit(Mothership_lasso)

RCI_df_anx2 <- Mothership_lasso_1 |>
  filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_dep2 <- Mothership_lasso_1 |>
  filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(CUDOS_pre),
    !is.na(CUDOS_post),
    CUDOS_pre > 20,
  ) |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

head(ANX_JT_smol)

view(DEP_JT_smol)
```

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have data
  filter(!is.na(Days_complete_1)) |>
  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
  )
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    # Anx_Responder = as.factor(
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
    #   )),
    # Dep_Responder = as.factor(
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
    #   )),
    # Treatment_Responder = as.factor(
    #   ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
    #   ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      # )))))))))))

@@

JT Numbers
```{r}
Mothership_post_anx <- left_join(Mothership_post,ANX_JT_smol, by = join_by(ID1 == ppid_anx)) |>
  mutate(
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, NA)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    )

Mothership_post_dep <- left_join(Mothership_post,DEP_JT_smol, by = join_by(ID1 == ppid_dep)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, NA)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    ))) |>
  filter(
    !is.na(Depression_Responder)
    )

@@

```{r}
#############            AnxDep_PrePost                 ##################

#7. create new DF with Varaibles we want

AnxDep_PrePost <- data.frame(cbind(Mothership_post_joined$ID1,
                                   Mothership_post_joined$Disorder_treat,
                                   Mothership_post_joined$BL_CUDOS,
                                   Mothership_post_joined$BL_CUXOS,
                                   Mothership_post_joined$CUDOS_pre,
                                   Mothership_post_joined$CUDOS_post,
                                   Mothership_post_joined$CUXOS_pre,
                                   Mothership_post_joined$CUXOS_post,
                                   #Extra stuff?
                                   Mothership_post_joined$Depression_Responder,
                                   Mothership_post_joined$Anxiety_Responder
                                   #Mothership_post$RESPONDER_FIGS
)) #%>%

@@

# Left join the FDR adjusted p.value
FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
FP.1se.dep$p.adjusted <- round(FP.1se.dep$p.adjusted,2)
FP.1se.dep$type = c("Depression")
FP.1se.dep
```

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Days_complete_1 + Days_not_attended_1 + Anxiety_C + Substance_C + 
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

FP_anx <- read_csv("~/Downloads/FP.1se.anx")
# FP_anx <- read_csv("~/Downloads/FP.1se.anx")

#Change the names of variables
FP_anx$Variable = Anx_reg_coefs2

@@

FP_anx <- FP_anx |>
  mutate(
    sig = ifelse(p.adjusted <= 0.05, 16,1)
  )
FP_anx

# Anx_reg_coefs[1:8] <- c("Days completed","Days not attended", "Co-Anxiety",         "Co-Substance",        "Post coping" ,     "Post pmh"     ,   
# "Post functioning"   ,     "Post wellbeing" )
# FP_anx$Variable = Anx_reg_coefs

Anx_reg_coefs
# FP_anx$Variable = c(                      
#                     "Days Completed","Days Not Attended","Anxiety Disroder","CUXOS Pre-score",
#                     "Coping Ability","Positive Mental Health", "Functioning"   
#                     )

FP_anx_m <- FP_anx |>
  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape= FP_anx$sig,
               # ifelse(FP_anx$p.adjusted <= 0.05, 
               #                        16, # colored ones for significant varaibles
               #                        1), # uncolored ones for insignificant varaibles
             size=4,show.legend = FALSE) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
  scale_color_manual(values = c("darkgrey","red"))+
  #change x axis name
  labs(
    x="Odds Ratio") +
    # title = "Odds of Anxiety Treatment Non-Response",
    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
                  xlim = c(.5,1.5)) +
  #add a line at 1 for reference 
   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
  #add anotations to help suggests what each side means.
  annotate("text", x = .6, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
  annotate("text", x = 1.5, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

@@

FP_dep <- read_csv("~/Downloads/FP.min.dep")

#rename the variables for the figure
FP_dep$Variable = Dep_reg_coefs
# FP_dep$Variable = c(
#                      "Days Not Attended",
#                     "CUDOS Pre-Score",
#                     "Coping Ability", "Positive Mental Health", "Functioning",
#                     "Sense of Well Being"
#                     )

>>>>

Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
  ))
Mothership_lasso_1 <- na.omit(Mothership_lasso)
dim(Mothership_lasso_1)

RCI_df_anx2 <- Mothership_lasso_1 |>
  filter(
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_dep2 <- Mothership_lasso_1 |>
  filter(
    !is.na(CUDOS_pre),
    !is.na(CUDOS_post),
    CUDOS_pre > 20,
  ) |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

view(ANX_JT_smol)
view(DEP_JT_smol)
```

@@

Mothership_post <- Mothership_post |>
  #1. Filter out scores for people not in the program / don't have data
  filter(!is.na(Days_complete_1)) |>
  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
  filter(!is.na(CUXOS_pre),
         !is.na(CUXOS_post),
         CUXOS_pre > 0,
         CUXOS_post >= 0,
         !is.na(CUDOS_pre),
         !is.na(CUDOS_post),
         CUDOS_pre > 0,
         CUDOS_post> 0
         ) |>
  mutate(
    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
  )
    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
    # Anx_Responder = as.factor(
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
    #   )),
    # Dep_Responder = as.factor(
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
    #   )),
    # Treatment_Responder = as.factor(
    #   ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
    #   ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
      # )))))))))))

@@

JT Numbers
```{r}
Mothership_post_anx <- left_join(Mothership_post,ANX_JT_smol, by = join_by(ID1 == ppid_anx)) |>
  mutate(
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    # Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, NA)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    )

Mothership_post_dep <- left_join(Mothership_post,DEP_JT_smol, by = join_by(ID1 == ppid_dep)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    # Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, NA)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    ))) |>
  filter(
    !is.na(Depression_Responder)
    )

@@

@@

# Left join the FDR adjusted p.value
FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
FP.1se.dep$p.adjusted <- round(FP.1se.dep$p.adjusted,2)
FP.1se.dep$type = c("Depression")
FP.1se.dep

write_csv(FP.1se.dep, "~/Downloads/FP.1se.dep")
```

@@

## min model
  glm_min_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Age_1 + Married + Days_complete_1 + Days_not_attended_1 + Anxiety_D + 
        Substance_C + Trauma_D + Other + Mood_C + BPD_Co_C + Substance_C + 
        CUXOS_pre + 
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")

@@

FP_anx <- read_csv("~/Downloads/FP.min.anx")
# FP_anx <- read_csv("~/Downloads/FP.1se.anx")

#Change the names of variables
FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
                    "Days Not Attended", "Anixety Disorder","Co-SUD", 
                    "Trauma Disorder", "Other Disorder", "Co-Mood Disorder", 
                    "Co-BPD", "CUXOS Pre", "Post Coping", 
                    "Post PMH", "Post Functioning", "Post Wellbeing")

@@

FP_anx <- FP_anx |>
  mutate(
    sig = ifelse(p.adjusted <= 0.05, 16,1)
  )

FP_anx_m <- FP_anx |>
  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=OR), shape= FP_anx$sig,
               # ifelse(FP_anx$p.adjusted <= 0.05, 
               #                        16, # colored ones for significant varaibles
               #                        1), # uncolored ones for insignificant varaibles
             size=3.5,show.legend = FALSE) +
  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5, show.legend = FALSE)+
  scale_color_manual(values = c("darkgrey","red"))+
  #change x axis name
  labs(
    x="Odds Ratio") +
    # title = "Odds of Anxiety Treatment Non-Response",
    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
                  xlim = c(.25,2.0)) +
  #add a line at 1 for reference 
   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
  #add anotations to help suggests what each side means.
  annotate("text", x = .6, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
  annotate("text", x = 1.5, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
  #Git rid of the Y - Axis
    theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())

@@

FP_dep <- read_csv("~/Downloads/FP.1se.dep")

#rename the variables for the figure

FP_dep$Variable = c(
                     "Days Not Attended",
                    "Post Coping", 
                    "Post PMH", "Post Functioning", "Post Wellbeing")
